\documentclass[12pt]{article}
\usepackage{graphicx, multirow}
\usepackage{amsmath, array}
\usepackage{fancyheadings, lastpage}
\usepackage{pdflscape ,anyfontsize}
\lhead{Group Project 07 – Project Plan}
\rhead{(Release) -Version 1.8}
\lfoot{Aberystwyth University / Computer Science}
\cfoot{}
\rfoot{\thepage of \pageref{LastPage}}
\begin{document}
\pagestyle{fancy}
\begin{flushleft}
\rule[0.5cm]{13.8cm}{0.1cm}
\end{flushleft}
{\fontsize{20}{20}\selectfont Group07 Project Plan and other Information}
\begin{flushleft}
\rule[0.5cm]{13.8cm}{0.1cm}
\end{flushleft}
\begin{flushleft}
\textit{Authors: } \newline
\textit{Config Ref:  } \newline
\textit{Date: } \newline
\textit{Version: } \newline
\textit{Status: }
\end{flushleft}

\vspace{10cm}
Department of Computer Science\newline
Aberystwyth University \newline
Aberystwyth \newline
Ceredigion \newline
SY23 3DB \newline
Copyright © Aberystwyth University 2013


\newpage
\tableofcontents{}
\newpage
\section{INTRODUCTION}
\subsection{Purpose}
This document displays how the project will be completed and any risks involved. It outlines
the requirements specified by the client as a series of documents.
\subsection{Scope}
This document should be read by all members of the group. It contains a list of tasks, the
schedule and risks involved in the project. It also details what the application and server will
be required to do.
\subsection{Objective}
\begin{itemize}
\item List the platforms to be used for the project
\item Provide a task schedule for the project
\item Provide a description of how the application and website will be used.
\item Provide a list of risks and how to reduce their effects
\item Provide an idea of the UI for the Android application and the website
\item Provide a description of how the application and website can be navigated
\end{itemize}
\newpage
\section{PROJECT OVERVIEW}
The proposed system is an application running on the Android operating system that will be used to
record walks for a particular user. The application will allow the user to start a recording of a new
walk and add points of interest to that walk, save the walk and view the walk later.
The website will allow the user to manage their uploaded walks and delete them as well as view
walks created by other users. The user also has to create an account via the website if they want to
be able to log-in on the Android application.
\subsection{Platforms}
\subsubsection{Android}
As stated by the client, the operating system used will be Android. This will be developed for
mobile devices. The operating system version will be 4.2
\subsubsection{HTML 5}
The website will be built using HTML 5 alongside CSS 2 and CSS 3. This will allow the latest
version of HTML to be used for the website.
\subsubsection{PHP}
PHP will be used to handle the communication between the mobile device and the server. It
will be run server side and is understood to a working level by the web programmers.
\subsubsection{MySQL}
The database will be built using MySQL. It shall store information about each walk and the
walk themselves. Information stored will include all points of interest added, their
associated long and short descriptions and any pictures taken.
\subsubsection{OpenSpace API}
This API by Ordinance Survey, will be used instead of Google Map’s. This is because this map
allows offline use, enabling recording whilst not connected to the internet as well as having
many useful features.
\subsection{Target Audience}
This application is aimed at Second Year Computer Science students. Precautions had to
be taken while designing the user interface to prevent the user from having to navigate
through too many screens.
\subsection{System Overview}

\subsubsection{Android Application}
This is the application. All modules here are running on the mobile device
\subsubsection{Online Offline}
This module handles the location where data is stored. If the user is connected to the
internet, it makes sure any uploads can be tied to the user.
\subsubsection{Walk List}
This module handles the listing of walks from the local database. (See Figure 4.3 and Figure 4.4)
\subsubsection{Map Screen}
This module handles the displaying of all visual elements from the walk. (See Figure. 4.8)
\subsubsection{Walk Recorder}
This module handles the storage of points of interest, the time taken for a walk and the walks location during recording.
\subsubsection{Walk Viewer}
This module handles loading of walks from the local database and converting them back into a visual form
\subsubsection{Local Database}
This module stores all locally saved walks and maps cache. It handles the retrieval and uploading of walks to the server.
\subsubsection{Database Protocol}
This module handles the conversion of database request to their required language such as from POST to HTTP for the website.
\subsubsection{Server}
This is the server that handles all requests between the database, website and android application
\subsubsection{Request Handler}
This module deals with linking data between users

\subsubsection{User Walks}
This module handles the retrieval and editing of walks of the associated user

\subsubsection{Other Walks}
This module handles all walks not owned by the user

\subsubsection{Physical Database}
This is the machine where all request are handled

\subsubsection{Website}
This module serves as the control for everything on the website
\subsubsection{Online Walk List}
This module handles all lists being displayed to anyone on the website

\subsubsection{Accounts}
This module handles the retrieval and creation of accounts
\subsubsection{Online Walk Viewer}
This module handles the conversion of data into visual form from broswser based on viewing of walks.

\section{USE CASE}
\subsection{Android}
\subsection{Website}
\subsection{Database}
\subsection{Interaction System}
The diagram above represents the interaction of the whole system. The user interacts with
both Android application and the website. The walks recorded by the user along with all the
other information like description and the photos, are stored in the database and can be easily
accessed later via the website or locally. Every action that creates or adds data is stored in the
database.
The Android application downloads a list of walks from the server and uploads walks from
the local database. The Android application does not have a direct link to the website.
Registration is done via the browser and logging in sends a query the database. The two way
interaction system is used to reflect this. The website and the database have a two way
interaction to give the administrator access to the data stored and the changes made on the
website have to be updated in the database. The website also pulls a list of walks from the
database and uploads any changes back into the database.
\newpage
\begin{landscape}
\subsection{Descriptions}
\begin{tabular}{|c|c|c|}
\hline
	Diagram Name & Use case name  & Description \\
\hline

 \multirow{4}{*}{Android} & \multicolumn{1}{|c|}{Create new walk} & \multicolumn{1}{|c|}{Allows the user to start recording a new walk} \\\cline{2-3} & \multicolumn{1}{|c|}{Save a walk 
} & \multicolumn{1}{|c|}{The user can save walks locally or upload them and save locally
if they have internet access}


\end{tabular}
\end{landscape}
\newpage
\section{ANDROID USER INTERFACE DESIGN}
\subsection{Start Screen}
\par{Displays only the program name, logo and group name. Tap to continue to main menu.
This screen may be replaced with a tutorial or help screen on first launch.}\newline
\textbf{\underline{NAVIGATION}} \newline 
Start $\rightarrow$ Main Menu (Figure 4.2)
\subsection{Main Menu}
\par{This screen is the main menu. It will allow users to view past walks, log-in or logout, view the
options and start new walks. Users will be returned to this screen after exiting or completing
a walk.}\newline
\textbf{\underline{NAVIGATION}} \newline 
Start Walk $\rightarrow$ New Walk Screen (Fig. 4.4) \newline
Sign in/Logout $\rightarrow$  Sign in screen / logout \newline
View Walks  $\rightarrow$ View Walks Screen (Fig. 4.3) \newline
Options  $\rightarrow$ Options Screen (Fig. 4.13) \newline
\subsection{View My Walks Screen}
\par{Above image is for viewing my walks. If a walk is selected, another screen opens with an
image of the walk. If the walk is uploaded an upload option is available. Other options are
load walk, delete walk and cancel. Tapping edit allows walks to be deleted. Deleting walks
only occurs locally and not on the server} \newline
\textbf{\underline{NAVIGATION}} \newline 
Back to main menu arrow $\rightarrow$ Main Menu (Fig. 4.2) \newline
Online Walks $\rightarrow$ View Online Walks Screen (Fig. 4.4) \newline
Select Walk $\rightarrow$ View My Walk Screen (Fig. 4.5) \newline
\subsection{View Online Walks Screen}
\par{This screen displays the walks downloaded from the server. These walks can be downloaded
from the server for use. Walks may be filtered in this screen based on location, number of
points of interest and viewed.}\newline
\textbf{\underline{NAVIGATION}} \newline 
Back to main menu arrow $\rightarrow$ Main Menu (Fig. 4.2) \newline
My Walks $\rightarrow$ View My Walks Screen (Fig. 4.3)\newline
\subsection{View My Walk Screen}
\par{This screen displays a small scrollable list of all points of interest on of the selected walk and
a small map of the areas covered by the walk. If they haven’t been uploaded, It walks can be
uploaded via this screen. Walks can also be loaded from here.} \newline
\textbf{\underline{NAVIGATION}} \newline 
Cancel $\rightarrow$ View My Walks Screen (Fig. 4.3) \newline
Load $\rightarrow$ Recording Screen With Walk (Fig. 4.10) \newline
\subsection{View Online Walk Screen}
\par{This screen is used to view other walks from the server. They can loaded from this screen. It
displays a list of Points of Interest for the walk and a small map displaying points of interest
from the walk}\newline
\textbf{\underline{NAVIGATION}} \newline 
Cancel $\rightarrow$ View Online Walks Screen (Fig. 4.4) \newline
Load $\rightarrow$ Recording Screen With Walk (Fig. 4.10) \newline
\subsection{New Walk Screen}
\par{This is the walk creation screen. It allows a short and long description to be added to a walk.} \newline
\textbf{\underline{NAVIGATION}} \newline
Back $\rightarrow$ Main Menu (Fig. 4.2) \newline
Start Walk $\rightarrow$  Recording Window (Fig. 4.4) \newline
\subsection{Recording Screen}
\par{This screen only displays the map around the users’ current location. When a point of
interest is added, it will be displayed as a pin on this screen. The options button will allow
the user to sign in/logout. When viewing a walk, only the option button and the swipe menu
will be available. Pinch zoom may be used instead of button zoom. If the user taps the pause
button, the recording will pause. If the user taps it again, the recording will resume. Holding
down the button will stop the recording and take the user to the walk complete screen. The
options menu will allow the user to exit the walk without saving.}\newline
\textbf{\underline{NAVIGATION}} \newline
Option $\rightarrow$ Option Menu \newline
Add Point of Interest $\rightarrow$ New Point of Interest Screen (Fig. 4.9) \newline
Stop $\rightarrow$ Walk Complete (Fig. 4.12) \newline
Swipe left across screen $\rightarrow$ Locations on Walk List (Fig. 4.11) \newline
\subsection{New Point of Interest}
\par{This screen is used to add a point of interest. It will appear semi-transparent over the map.
Adding images will open a dialogue asking whether to go to the photo library or the camera
app, allowing images to be added. Images will appear between the short and long
description and can be removed from here. Pressing save stores the point of interest but can
be removed later.} \newline
\textbf{\underline{NAVIGATION}} \newline
Cancel $\rightarrow$ Recording screen with walk (Fig. 4.10) or Recording screen (Fig. 4.9) \newline
Add Image $\rightarrow$ Dialogue for Camera or Photo Library \newline
Save $\rightarrow$ Recording screen with walk (Fig. 4.10) or Recording screen (Fig. 4.9) \newline
\subsection{Recording Screen With Walk}
\par{This screen is the default recording screen. All points of interest are noted as a pin on the
screen. Tapping the pin displays the long and short description and any images of the point
of interest. When a walk is stopped the user is prompted to save the walk. Only signed in
users can upload a walk to the server. When viewing a walk, only the option button and the
swipe menu will be available.} \newline
\textbf{\underline{NAVIGATION}} \newline
Option $\rightarrow$ Option Menu \newline
Add Point of Interest $\rightarrow$ New Point of Interest Screen (Fig. 4.9) \newline
Stop $\rightarrow$ Walk Complete (Fig. 4.12) \newline
Swipe left across screen $\rightarrow$ Locations on Walk List (Fig. 4.11) \newline
\subsection{Walk Complete}
This screen allows the user to save a walk. If upload is pressed, the walk is saved then uploaded
to the server provided the user is signed in. This screen should be unavailable if there are no
points of interest to prevent uploading or saving an empty walk. This screen also shows the time
taken to complete a walk, the name of the walk, the number of points of interest added and the
location of the walk. \newline
\textbf{\underline{NAVIGATION}} \newline
Cancel $\rightarrow$ Recording Screen with walk (Fig. 4.10) \newline
Save $\rightarrow$ View My Walks Screen (Fig. 4.3) \newline
Upload $\rightarrow$ View My Walks Screen (Fig. 4.3) \newline
\subsection{Options Screen}
\par{This screen is only accessible from the main menu. It allows the user to calibrate their compass
and check the GPS is accurate. They can also register an account which will open the browser
and redirect them to the website registrations screen.} \newline
\textbf{\underline{NAVIGATION}} \newline
Back to Main Menu $\rightarrow$ Main Menu (Fig. 4.2)\newline
Register Account $\rightarrow$  Registration Page in phone browser (Fig. 5.4) \newline
Calibrate GPS $\rightarrow$ GPS and Compass Calibration screen. \newline
\section{WEBSITE USER INTERFACE DESIGN}
\subsection{Home Page}
\par{This is the homepage of the website. From here the user can find information about the
application and a link to where the mobile application can be downloaded. They can also
log-in or register via this page and can view walks.} \newline
\textbf{\underline{NAVIGATION}} \newline
Log-in $\rightarrow$ Log-in Page (Fig. 5.3) \newline
Register $\rightarrow$ Registration Page (Fig. 5.4) \newline
View Walks $\rightarrow$ View Walks Page (Fig. 5.2)\newline
\subsection{View Walks Page}
\par{The user can view all uploaded walks via this screen. From here the user can see a small map
overview of the walk and the short description of the points of interest. If the user is signed in,
they can view their walks from this page.}\newline
\textbf{\underline{NAVIGATION}} \newline
Click on Walk $\rightarrow$ Walk Page (Fig. 5.6) \newline
Log-in $\rightarrow$ Log-in Page (Fig. 5.3) \newline
Register $\rightarrow$ Registration Page (Fig. 5.4) \newline
View My Walks $\rightarrow$ View My Walks Page (Fig. 5.5) \newline
Home $\rightarrow$ Home Page (Fig. 5.1) \newline
\subsection{Log-in Page}
\par{The user can log-in to their account via this page. Clicking the log-in button will refresh the
current page. If the user doesn’t have an account, they can click register. Clicking outside the
box will take them back without logging in.}\newline
\textbf{\underline{NAVIGATION}} \newline
Log-in $\rightarrow$ Previous Page \newline
Register $\rightarrow$ Registration Page (Fig. 5.4) \newline
Click Outside Box $\rightarrow$ Previous Page \newline
\subsection{Registration Page}
\par{This page allows new users to create an account. Existing users may also click log-in via this
page. New users must perform an authentication to prevent automated accounts being
created.} \newline
\textbf{\underline{NAVIGATION}} \newline
Register $\rightarrow$ View Walks Page (Fig. 5.2) \newline
Log-in $\rightarrow$ Log-in Page (Fig. 5.3) \newline
Home $\rightarrow$ Home Page (Fig. 5.1) \newline
\subsection{View My Walks Page}
\par{This page lets users view their uploaded walks. The user can delete their walk from this
screen. They can also see the time taken to delete a walk. To sign out or access account
settings, a menu will be available by clicking their username. Users can also view other walks
separately.} \newline 
\textbf{\underline{NAVIGATION}} \newline
Sign out $\rightarrow$ View Walks Page (Fig. 5.2) \newline
Click on Walk $\rightarrow$ Walk Page (Fig. 5.6) \newline
View Walks $\rightarrow$ View Walks Page (Fig. 5.2) \newline
Home $\rightarrow$ Home Page (Fig. 5.1) \newline
\subsection{Walk Page}
\par{This page displays a map overview of the walk, the average time taken to complete the walk
and the long and short descriptions. The first image from every point of interest is displayed
at the bottom of the screen.} \newline
\textbf{\underline{NAVIGATION}} \newline
Click on Image $\rightarrow$ Point of Interest Image Page (Fig. 5.8) \newline
Click Pin on Map $\rightarrow$ Point of Image Selected Page (Fig. 5.7) \newline
Delete Walk (if owner) $\rightarrow$ View Walks Page (Fig. 5.2) \newline
View Walks $\rightarrow$ View Walks Page (Fig. 5.2) \newline
Register $\rightarrow$ Registration Page (Fig. 5.4) \newline
Log-in $\rightarrow$ Log-in Page (Fig. 5.3) \newline
Home $\rightarrow$ Home Page (Fig. 5.1) \newline
Sign out (if logged in) $\rightarrow$ View Walks Page (Fig. 5.2) \newline
\subsection{Point of Interest Selected Page}
\par{Clicking on a pin on the map opens this page. The selected pin is also highlighted. The page
displays the average time taken from the start of the walk to arrive at this point of interest.
If there are any images taken from this point of interest, the user is can view them. If the
user owns this walk, they will be able to edit the descriptions and add more images. The
latitude and longitude of this point of interest is also displayed opposite the short
description.} \newline 
\textbf{\underline{NAVIGATION}} \newline
Edit POI $\rightarrow$ Edit Point of Interest Page (Fig. 5.9) \newline
Delete Walk (if owner) $\rightarrow$ View My Walks Page (Fig. 5.5) \newline
Click on Image $\rightarrow$ Point of Interest Image Page (Fig. 5.8)\newline
Click Pin on Map $\rightarrow$ Point of Image Selected Page (Fig. 5.7) \newline
View Walks $\rightarrow$ View Walks Page (Fig. 5.2) \newline
Register $\rightarrow$ Registration Page (Fig. 5.4) \newline
Log-in $\rightarrow$ Log-in Page (Fig. 5.3) \newline
Home $\rightarrow$ Home Page (Fig. 5.1) \newline
Sign out (if logged in) $\rightarrow$ View Walks Page (Fig. 5.2) \newline
\subsection{ Point of Interest Image Page}
\par{This simply enlarges the image clicked. Clicking outside the box minimizes the image back
into the tray.}\newline 
\textbf{\underline{NAVIGATION}} \newline
Click Outside Image $\rightarrow$ Previous Page \newline
\subsection{Edit Point of Interest Page}
\par{This page is only available if the user owns the walk. It allows users to add more images to
the point of interest as well as edit the descriptions. Clicking anything other than save will
undo any changes including image uploads.} \newline
\textbf{\underline{NAVIGATION}} \newline
Save $\rightarrow$ Walk Page (Fig. 5.6) \newline
Delete Walk (if owner) $\rightarrow$ View My Walks Page (Fig. 5.5) \newline
Click on Image $\rightarrow$ Point of Interest Image Page (Fig. 5.8) \newline
Click Pin on Map $\rightarrow$ Point of Image Selected Page (Fig. 5.7) \newline
View Walks $\rightarrow$ View Walks Page (Fig. 5.2) \newline
Register $\rightarrow$ Registration Page (Fig. 5.4) \newline
Log-in $\rightarrow$ Log-in Page (Fig. 5.3) \newline
Home $\rightarrow$ Home Page (Fig. 5.1) \newline
Sign out (if logged in) $\rightarrow$ View Walks Page (Fig. 5.2) \newline
\section{NAVIGATION OVERVIEW}
\subsection{Android}
\par{Start screen is the entry point. All navigation is done via buttons and icons unless otherwise
stated}
\subsection{Website}
Home page is the entry point. All pages link back to the home page
\section{GANTT CHART}
\section{RISK ASSESSMENT}
\begin{tabular}{|p{2cm}|c| p{10cm}|}
\hline
	Event  & Risk  & Mitigation \\
\hline
	Git Downtime  & Low & All work should be backed up on multiple devices, preferably the University of Aberystwyth M: Drive and local backup locations.
The deputy team leader will take up responsibilities
\\
\hline
	Absence of Team Leader & Low 
 & The deputy team leader will take up responsibilities as required.
\\
\hline
	QA Manager 
Absence 
 &Low 
 & Team leader or deputy team leader will take up responsibilities as required.
\\
\hline
	Poor Quality 
Work 
 & Low 
 & All work must be verified and monitored by both the QA Manager and the
Team Leader. Deadlines for tasks are given before official deadlines to provide
a window in which work is brought up to standard.
\\
\hline
	61 & 62 & 63\\
\hline
	71 & 72 & 73\\
\hline
	81 & 82 & 83\\
\hline
	91 & 92 & 93\\
\hline
	101 & 102 & 103\\
\hline
	111 & 112 & 113\\
\hline
	121 & 122 & 123\\
\hline
	131 & 132 & 133\\
\hline
	141 & 142 & 143\\
\hline
	151 & 152 & 153\\
\hline
	161 & 162 & 163\\
\hline
	171 & 172 & 173\\
\hline
	181 & 182 & 183\\
\hline
	191 & 192 & 193\\
\hline
	201 & 202 & 203\\
\hline
\end{tabular}

\end{document}